A Simple Minibatch Acceptance Test for MCMC

### 2016-05-17 nips_2016.tex
adding exp

\PassOptionsToPackage{numbers, compress}{natbib}
\usepackage{nips_2016}
% to compile a camera-ready version, add the [final] option, e.g.:
%\usepackage[final]{nips_2016}

@@

\author{
  John Canny \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{canny@berkeley.edu}
  \And
  Haoyu Chen \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{haoyuchen@berkeley.edu}
  \And
  Daniel Seita \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{seita@berkeley.edu}
  \And
  Xinlei Pan \\
  Department of Bioengineering \\
  University of California, Berkeley \\
  \texttt{xinleipan@berkeley.edu}
  \And 
  Biye Jiang \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{bjiang@berkeley.edu}
}

@@

\subsection{Neural Network Optimization}\label{ssec:nets}
In this experiment, we apply about mini-batch MH testing with SGHMC proposer to sample the parameter instances from 
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}

>>>>

\PassOptionsToPackage{numbers, compress}{natbib}
%\usepackage{nips_2016}
% to compile a camera-ready version, add the [final] option, e.g.:
\usepackage[final]{nips_2016}

@@

\author{
  Haoyu Chen \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{haoyuchen@berkeley.edu}
  \And
  Daniel Seita \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{seita@berkeley.edu}
  \And
  Xinlei Pan \\
  Department of Bioengineering \\
  University of California, Berkeley \\
  \texttt{xinleipan@berkeley.edu}
  \And 
  Biye Jiang \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{bjiang@berkeley.edu}
  \And
  John Canny \\
  Department of Computer Science \\
  University of California, Berkeley \\
  \texttt{canny@berkeley.edu}
}

@@

\subsection{Neural Network Optimization}\label{ssec:nets}
In this experiment, we apply about mini-batch MH testing with SGHMC proposer to sample the parameter instances from a fully connected neural network.
\begin{figure}[ht]
  \centering
  \fbox{\rule[-.5cm]{0cm}{4cm} \rule[-.5cm]{4cm}{0cm}}
  %\includegraphics[width=0.5\linewidth]{empty}
  \caption{This will hopefully show results for neural networks on BIDMach.}
\end{figure}
